Growing Up with Nell: A Narrative Interface for Literacy

### 2012-03-14 paper.tex
Turn authors back on, shrink TurtleScript to keep everything on 4 pages.
Attempt to make borders on TurtleScript diagram more clear.
Turn authors off, resubmit with darker outlines for TurtleScript.
Avoid unmotivated praise, which demotivates.
See http://www.alfiekohn.org/parenting/gj.htm (from Mitch)
and
http://www.amazon.com/Self-theories-Motivation-Personality-Development-Psychology/dp/1841690244/
(from Caroline).

As she traces the R, it comes to life and gallops across the screen.
\textit{``Run starts with R.  Roger the R runs across the Red Rug.
Roger has a dog named Rover.''}  Rover barks: \textit{``Ruff! Ruff!''}  The
Princess asks, \textit{``Can you find something Red?''} and Rahel uses the
camera to photograph berries on a nearby bush.

\textit{``Very good!  You are a smart girl!''}

@@

For example, the \textit{story-intro-group}
used in Figure~\ref{fig:rules} defaults to a low priority so that
continuing a story in progress is preferred above starting a new story.
When a story module is completed, several new story openings will be in
conflict.  The resolution scene for \textit{story-intro-group} may bring us
to the controls of an airship which flies between locations
corresponding to the various story continuations.  In that set of
scenes, the child may eventually decide to fly to Mathland to hear the
next episode in her agent Mathis' adventure, which would bump up the
appropriate scene's priority to allow us to make the transition
without further conflict.

@@

% XXX refer to TurtleScript excerpt in figure somewhere here.
\begin{figure}
\centering
\epsfig{file=turtlescript.eps, height=1.5in}
\caption{Factorial function in TurtleScript.}\label{fig:turtlescript}
\end{figure}

>>>>

As she traces the R, it comes to life and gallops across the screen.
\textit{``Run starts with R.  Roger the R runs across the Red Rug.
Roger has a dog named Rover.''}  Rover barks: \textit{``Ruff! Ruff!''}  The
Princess asks, \textit{``Can you find something Red?''} and Rahel uses the
camera to photograph a berry on a nearby bush.

\emph{``Good work!  I see a little red \underline{here}.  Can you find
something \emph{big} and red?''}
% avoid excessive/unmerited praise
% try to say *what* you like, rather than just vague praise
% provide quality feedback, encourage the kid to max out the meter on
% their own (ie, making the kid proud of himself for doing well is
% better than telling him they're doing well)

@@

For example, the \textit{story-intro-group}
used in Figure~\ref{fig:rules} defaults to a low priority so that
continuing a story in progress is preferred above starting a new story.
When a story module is completed, several new story openings will be in
conflict.  The resolution scene for \textit{story-intro-group} may bring us
to the controls of an airship which flies between locations
corresponding to the various story continuations.  In that set of
scenes, the child may eventually decide to fly to Mathland to hear the
next episode in her agent Mathis' adventure, which would bump up the
appropriate scene's priority to make the transition
without further conflict.

@@

% XXX refer to TurtleScript excerpt in figure somewhere here.
\begin{figure}
\centering
\epsfig{file=turtlescript-2.eps, height=1.3in}
\caption{Factorial function in TurtleScript.}\label{fig:turtlescript}
\end{figure}
